Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-06-18 paper/IJCAI19/paper.tex
ijcai editor mandatory reviews

% the following package is optional:
\usepackage{latexsym}

@@

\author{
Sofia Reis$^1$
\and
Rui Abreu$^1$\and
Marcelo D'Amorim$^2$\affiliations
$^1$IST, University of Lisbon \& INESC-ID, Portugal\\
\emails
sofia.o.reis@tecnico.ulisboa.pt,
rui@computer.org\\
$^2$Federal University of Pernambuco, Brazil\\
\emails
damorim@cin.ufpe.br
}

%\hypersetup{draft}
\begin{document}

@@

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at {\footnotesize\url{https://github.com/MozillaSecurity/lithium}} (Accessed \today)}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in
number of lines---of chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has $1,000$ lines, Lithium sets the
initial chunk size to $512$ lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} 
(Accessed \today)}.

@@

\begin{figure}[t!]

  \centering
  \begin{subfigure}{0.5\textwidth}
    {\def\arraystretch{0.9}\setlength{\tabcolsep}{3pt}
      \begin{tabular}{c|ccccc|c}
        $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
        $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
        $t_2$         & 0 & 1 & 1 & 1 & 1 &\xmark  \\
        $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
        $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
        $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark \\
        \hline
      \end{tabular}
      \quad
      $\Rightarrow$
      \quad
      \begin{tabular}{c|ccccc|c}
        $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
        $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
        $t_2$         & 0 & 1 & {\cellcolor{Gray} 0} & {\cellcolor{Gray} 0} & 1 &\xmark  \\
        $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
        $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
        $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark  \\
        \hline
      \end{tabular}
    }
    \caption{Spectra update.}
    \label{fig:ds-reduction}
  \end{subfigure}

@@

\begin{table}[h]
  \small
  \centering
  \setlength{\tabcolsep}{4pt}
  \begin{tabular}{lrrr}
    \toprule
    Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
    \midrule
    \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
    \cmath{}           & 306,276  & 26,797 & 104     \\   %\comments{& 177   &  -}\\
    %      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
    \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
    \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
    \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
    \bottomrule
  \end{tabular}
  \caption {Characterization of \dfj{} subjects.}
  \label{tab:df4j}
\end{table}
\normalsize

@@

\subsubsection{\label{rq:1}RQ1: \textit{\rqone}}

@@

\begin{table}[h]
  \small
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr}
		\toprule
		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
		\midrule

@@

\subsubsection{RQ2: \textit{\rqtwo}}
\label{rq:2}

@@

\begin{table}[h]
	\small
	\setlength{\tabcolsep}{3pt}
	\centering
\begin{tabular}{l|rr|rr}
		 \toprule
       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
		\midrule
		 \lang{}         &   84.6   & 96.9 & 84.6 & 96.9  \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
		Total         & 79.6 & 86.5 & 83.5 & 90.4\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty
    statements appears at the report of the technique. Higher is better.}
  \label{table:fsws}
\end{table}

\subsubsection{RQ3: \textit{\rqthree}}

@@

\begin{figure}[h]
		\centering
		\includegraphics[width=0.45\textwidth]{figures/performance.png}
		\vspace{-0.4cm}
		\caption{Delta Cost of Diagnosis ($\Delta{}C$) per $k$}
		\label{fig:diagnosis}
\end{figure}

@@

\begin{figure}[h]
		\vspace{-0.2cm}
		\centering
		\includegraphics[width=0.45\textwidth]{figures/boxplot.png}
		\vspace{-0.4cm}

		\caption{Distributions of $\Delta{}C$ considering all cases where \combpar{k}
        outperformed the baseline}
		\label{fig:boxplot}
		\vspace{-0.2cm}
\end{figure}

@@

\begin{table}[h]
	\tiny
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
     \toprule
  & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
  & SFL  & \comb\       & SFL                & \comb\              \\ \midrule
Mean  & \textbf{779.3} (584.3) & \textbf{738.2} (679.7)   &  \textbf{630.6} (516.4)    & \textbf{611.9} (614.0)   \\ \midrule
Median & \textbf{187.7} (49.4) & \textbf{167.2} (69.3)      & \textbf{167.2} (53.0) & \textbf{107.5} (56.9)\\ \midrule
Variance & \textbf{1218.3} (1223.1) & \textbf{1186.3} (1352.4)  &  \textbf{1058.4} (1148.1) &  \textbf{1048.6} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.67 \\ $p$ = 9.64 x $10^{-15}$} & \makecell{$W$ = 0.66 \\ $p$ = 5.59 x $10^{-15}$} & \makecell{$W$ = 0.63 \\ $p$ = 1.09 x $10^{-15}$} &  \makecell{$W$ = 0.63 \\ $p$ = 8.95 x $10^{-16}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 175.18 \\ p-value = 9.71 x $10^{-38}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests for $C$}
  \label{table:st}
\end{table}

@@

\begin{figure}[h]
	\vspace{-2cm}
		\includegraphics[width=0.48\textwidth]{figures/heatmap_seg_result.png}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
		\vspace{-0.3cm}
\end{figure}

@@

This material is based upon work supported by Fundação para a Ciência 
e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017, and by national funds also through FCT with reference UID/CEC/50021/2019.

{
  \small
  \balance
  \bibliographystyle{named}
  \bibliography{paper}
}

>>>>

% the following package is optional:
\usepackage{latexsym}
\urlstyle{rm}

@@

\author{
Sofia Reis$^1$
\and
Rui Abreu$^1$\and
Marcelo d'Amorim$^2$\affiliations
$^1$IST, University of Lisbon \& INESC-ID, Portugal\\
$^2$Federal University of Pernambuco, Brazil\\
\emails
sofia.o.reis@tecnico.ulisboa.pt,
rui@computer.org; damorim@cin.ufpe.br\\
}

\begin{document}

@@

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at {\footnotesize\url{https://github.com/MozillaSecurity/lithium}} (Accessed \today)}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in
number of lines---of chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has $1,000$ lines, Lithium sets the
initial chunk size to $512$ lines. Then, the tool starts a local search looking
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed.
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. % Proofs of the algorithm complexity can be found
% elsewhere\footnote{Lithium complexity available at \mbox{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md}
% (Accessed \today)}.

@@

\begin{figure}[tb]
  \centering
  \begin{subfigure}{0.5\textwidth}
    {\def\arraystretch{0.9}\setlength{\tabcolsep}{3pt}
      \begin{tabular}{c|ccccc|c}
        $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
        $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
        $t_2$         & 0 & 1 & 1 & 1 & 1 &\xmark  \\
        $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
        $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
        $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark \\
        \hline
      \end{tabular}
      \quad
      $\Rightarrow$
      \quad
      \begin{tabular}{c|ccccc|c}
        $\mathcal{T}$ & $c_1$    & $c_2$   & $c_3$ & $c_4$ &  $c_5$   & $e$    \\ \hline
        $t_1$         & 1 & 0 & 1 & 1 & 0 &\cmark  \\
        $t_2$         & 0 & 1 & {\cellcolor{Gray} 0} & {\cellcolor{Gray} 0} & 1 &\xmark  \\
        $t_3$         & 1 & 0 & 1 & 0 & 0 &\xmark  \\
        $t_4$         & 0 & 1 & 0 & 0 & 1 &\cmark  \\
        $t_5$         & 1 & 0 & 0 & 1 & 1 &\cmark  \\
        \hline
      \end{tabular}
    }
    \caption{Spectra update.}
    \label{fig:ds-reduction}
  \end{subfigure}

@@

\begin{table}[tb]
  \small
  \centering
  \setlength{\tabcolsep}{4pt}
  \begin{tabular}{lrrr}
    \toprule
    Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
    \midrule
    \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
    \cmath{}           & 306,276  & 26,797 & 104     \\   %\comments{& 177   &  -}\\
    %      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
    \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
    \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
    \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
    \bottomrule
  \end{tabular}
  \caption {Characterization of \dfj{} subjects.}
  \label{tab:df4j}
\end{table}
\normalsize

@@

\subsubsection{\label{rq:1}RQ1: \rqone}

@@

\begin{table}[tb]
  \small
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr}
		\toprule
		Project             &  \multicolumn{1}{c}{$k=5$} & \multicolumn{1}{c}{$k=10$} \\ %\combpar{5}  & \combpar{10}
		\midrule

@@

\subsubsection{RQ2: \rqtwo}
\label{rq:2}

@@

\begin{table}[tb]
	\small
	\setlength{\tabcolsep}{3pt}
	\centering
\begin{tabular}{l|rr|rr}
		 \toprule
       & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
		 Project        &   \sfl{}   & \comb &   \sfl{}   & \comb\\
		\midrule
		 \lang{}         &   84.6   & 96.9 & 84.6 & 96.9  \\
		\cmath{}           & 81.7 & 89.4 & 85.6 & 95.2 \\
		\chart{}           & {\cellcolor{Gray} 84.6} & {\cellcolor{Gray}76.9} & {\cellcolor{Gray}92.3} & {\cellcolor{Gray}84.6}\\
		\jtime{}           & 77.8 & 81.5 & 81.5 & 85.2\\
		\mockito{}           & 63.2 & 71.1 & 71.1 & 78.9\\   \midrule
		Total         & 79.6 & 86.5 & 83.5 & 90.4\\
		\bottomrule
	\end{tabular}
  \caption {Number of faults where at least one of the faulty
    statements appears at the report of the technique. Higher is better.}
  \label{table:fsws}
\end{table}

\subsubsection{RQ3: \rqthree}

@@

\begin{figure}[tb]
		\centering
		\includegraphics[width=0.42\textwidth]{figures/performance.png}
		\vspace{-0.4cm}
		\caption{Delta Cost of Diagnosis ($\Delta{}C$) per $k$}
		\label{fig:diagnosis}
\end{figure}

@@

\begin{figure}[tb]
		\vspace{-0.2cm}
		\centering
		\includegraphics[width=0.42\textwidth]{figures/boxplot.png}
		\vspace{-0.4cm}
		\caption{Distributions of $\Delta{}C$ considering all cases where \combpar{k}
        outperformed the baseline}
		\label{fig:boxplot}
		\vspace{-0.2cm}
\end{figure}

@@

\begin{table}[tb]
    \begin{adjustwidth}{-.5in}{-.5in}

	\scriptsize
	\centering
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}c|c|c|c|c@{}}
     \toprule
  & \multicolumn{2}{c|}{$k=5$} & \multicolumn{2}{c}{$k=10$} \\
  & SFL  & \comb\       & SFL                & \comb\              \\ \midrule
Mean  & \textbf{779.3} (584.3) & \textbf{738.2} (679.7)   &  \textbf{630.6} (516.4)    & \textbf{611.9} (614.0)   \\ \midrule
Median & \textbf{187.7} (49.4) & \textbf{167.2} (69.3)      & \textbf{167.2} (53.0) & \textbf{107.5} (56.9)\\ \midrule
Variance & \textbf{1218.3} (1223.1) & \textbf{1186.3} (1352.4)  &  \textbf{1058.4} (1148.1) &  \textbf{1048.6} (1294.9) \\ \midrule
Shapiro-Wilk &\makecell{$W$ = 0.67 \\ $p$ = 9.64 x $10^{-15}$} & \makecell{$W$ = 0.66 \\ $p$ = 5.59 x $10^{-15}$} & \makecell{$W$ = 0.63 \\ $p$ = 1.09 x $10^{-15}$} &  \makecell{$W$ = 0.63 \\ $p$ = 8.95 x $10^{-16}$}  \\ \midrule
Friedman & \multicolumn{4}{c}{\makecell{$\chi^{2}$ = 175.18 \\ p-value = 9.71 x $10^{-38}$}} \\
\bottomrule
\end{tabular}
  \caption {Statistical tests for $C$}
  \label{table:st}
  \end{adjustwidth}
\end{table}

@@

\begin{figure}[tb]
	\vspace{-2cm}
		\includegraphics[width=0.5\textwidth]{figures/heatmap_seg_result.png}
		\caption{Siegel post-hoc analysis results}
		\label{fig:performance}
		\vspace{-0.2cm}
\end{figure}

@@

This material is based upon work supported by Fundação para a Ciência 
e a Tecnologia (FCT), with the reference PTDC/CCI-COM/29300/2017, and by 
national funds also through FCT with reference UID/CEC/50021/2019.
This research was partially funded by INES 2.0, FACEPE grants PRONEX 
APQ 0388-1.03/14 and APQ-0399-1.03/17, and CNPq grant 465614/2014-0.

{
  \bibliographystyle{named}
  \bibliography{paper}
}
